How to Avoid OOTA Without Really Trying

### 2024-10-09 paper/ootavacuous.tex
ootavacuous: Remove lingering "Tagline" notes
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
ootavacuous: Connect witnesses to perturbations
Also save a line while in the area.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\emph{Tagline: ``How to think about semantic dependencies.'' }

@@

\emph{ Tagline: ``How to think about OOTA.'' }

@@

@@

A corollary of this result is that if an implementation's compiler
either
(1)~uses per-thread analysis and treats atomic objects as quasi
volatile, or
(2)~uses global analysis and treats atomic objects as volatile,
then programs produced by that implementation will never exhibit OOTA.
Thus the implementation will automatically comply with full C++, even
though it may have been designed only to comply with loose C++.

>>>>

@@

@@

These witnesses generalize the notion of
perturbations~\cite{PaulEMcKenney2016OOTA}.

@@

A corollary of this result is that if an implementation's compiler
either
(1)~uses per-thread analysis and treats atomic objects as quasi
volatile, or
(2)~uses global analysis and treats atomic objects as volatile,
then programs produced by that implementation will never exhibit OOTA.
Thus the implementation will automatically comply with full C++, even
if it was designed only to comply with loose C++.
